---
title: "ReadMe"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# lmTutorial

## Excercise for the understanding lm on the states dataset

The dataset compares the data from 6 states , containing information about the region, population, are, density , csat, vsat, percent, expense

The Excercise involves changing the lm equation to include a new interation to see how the csat value is affected



```{r}
setwd("C:/Users/s/Downloads/linear_regression/linear_regression")
getwd() # where am I?
list.files("dataSets") # files in the dataSets folder

## Load the states data
## ────────────────────────

# read the states data
states.data <- readRDS("dataSets/states.rds") 
```


##   1. Add on to the regression equation that you created in exercise 1 by
##      generating an interaction term and testing the interaction.

```{r}
sat.expense.metro.by.percent <- lm(csat ~ expense*metro,
                             data=states.data) 

print(coef(summary(sat.expense.metro.by.percent)))
```

Then we add  region to the model

```{r}
sat.expense.region.metro.by.percent <- lm(csat ~ expense*metro*region,
                                    data=states.data)

```

Looking at the summary it seems like there is significant difference between the regions


# compare both using the anova() function

```{r}
anova(sat.expense.metro.by.percent, sat.expense.region.metro.by.percent)
```